Truthfulness Verification System

### 2011-02-23 trunk/proposal/paper.tex
added Filipino example

\subsubsection{Application of Machine learning algorithms}
Though usage of machine learning algorithm seems to be very exciting approach at
this point, we are also skeptical about it. Supervised classifiers might not be
benficial for us due to the limited dataset for training and the potentialy
unlimited variety of inputs to classify. However, if we can use Graph
Based Partially Supervised Learning\cite{conf/acl/CelikyilmazTH09} or
Spreading Activation \cite{Cohen1987255} on the information extacted from the
rich ontologies is something we plan to explore.

>>>>

\subsubsection{Finding Sense of Words}
To classify a statement as true or false we need to get the semantic of sense of the words of the sentences. For example consider the following sentence.

\emph{"Tom Hanks was the lead actress in the movie sleepless in Seattle"}

Now our query results from ontologies will give us the fact that Tom hanks is a male actor. Now using wordnet we will be able to find that actress means female actor. So by simple inference our system will be able to classify the above example as untruthful.

However, finding sense of words in a complex problem in general and not easy to solve for all cases all the time. For example, consider the following sentence.

\emph{"Filipino is the primary language of Philipines"}

now Wikipedia has "Filipino is the national language of Philipines". Both sentences have same meaning but it is not easy to relate primary with national because they are not each others synonym as separate words. They become synonym depending on the context they are used such as above example. At this point, we don't have any generic strategy to handle these kind of situations. However, we will explore more to find possible ways to solve these problems. And one possible way may be to use some natural language processing techniques. Specifically, we will look into NLTK library to solve these kind of issues.

\subsubsection{Use of Co-reference Program}
Totha: please write up two lines here

\subsubsection{Application of Machine learning algorithms}
Though usage of machine learning algorithm seems to be a good approach at
this point. Consider the following example.

\emph{"Tom Hanks was the lead actress in the movie sleepless in Seattle"}

Now If the algorithm can learn that Tom hanks is a male and so he can't be an actress then our system should be able to classify the above statement as false.

However, we will need to explore more to be sure that we can apply machine learning algorithms successfully. Supervised classifiers might not be beneficial for us due to the limited dataset for training and the potentially unlimited variety of inputs to classify. However, if we can use Graph Based Partially Supervised Learning\cite{conf/acl/CelikyilmazTH09} or Spreading Activation \cite{Cohen1987255} on the information extracted from the rich ontologies is something we plan to explore.

\section{Conclusion}
It this paper, we described current system for truthfulness verification of statements found in the web called T-Verifier and described the possible improvements to the current system. We will primarily use authentic information sources such as Wikipedia and Ontologies extracted from Wikipedia such as FreeBase, DBPedia, and YOGA to found the truthfulness of doubtful statements.
